Local Spectral Clustering of Density Upper Level Sets

### 2019-06-04 neurips/local_spectral_density_clustering_arxiv.tex
format changes

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
     \usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2019}

%\PassOptionsToPackage{numbers}{natbib}
\usepackage{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2019}

@@

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{float}
\usepackage[export]{adjustbox}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{xr-hyper}
\usepackage{hyperref}
\usepackage[reqno]{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[parfill]{parskip}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{bm}
\usepackage{mathtools}

@@

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

\newtheoremstyle{aldenrmrk}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\itshape} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenrmrk}
\newtheorem{remark}{Remark}
%%%%%% End Alden

\title{Local Spectral Clustering of Density Upper Level Sets}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{
Alden Green \And
Sivaraman Balakrishnan \And
Ryan J. Tibshirani}

\begin{document}
\maketitle

\vspace{0.1in}
\begin{abstract}
We analyze Personalized PageRank (PPR), a local spectral method for clustering,
which extract clusters using locally-biased random walks around a user-specified
seed node.  In constrast to previous work, we adopt a traditional statistical
learning setup, where we obtain samples from an unknown distribution, and aim to
identify connected regions of high-density (density clusters).  We prove that
PPR, run on a neighborhood graph, extracts sufficiently salient density
clusters. We also provide empirical support for our theory.
\end{abstract}

\section{Introduction}
\label{sec: introduction}

@@

\clearpage
\appendix

In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.

@@

	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
	\begin{equation}
	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
	\end{equation}

>>>>

\documentclass[11pt,twoside]{article}
\usepackage{fancyhdr}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue,bookmarks=false]{hyperref}
\usepackage{amsfonts,epsfig,graphicx}
\usepackage{afterpage}
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{fullpage}
\usepackage[T1]{fontenc} 
\usepackage{epsf} 
\usepackage{graphics} 
\usepackage{amsfonts,amsmath}
\usepackage[sort,numbers]{natbib} 
\usepackage{psfrag,xspace}
\usepackage{color,etoolbox}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-6cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}
\addtolength{\textheight}{-1.1\headheight}
\addtolength{\textheight}{-\headsep}
\addtolength{\textheight}{-\footskip}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}

\newtheorem{theorem}{Theorem} 
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem*{remark}{Remark}

@@

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{float}
\usepackage[export]{adjustbox}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{xcolor}
%\usepackage{xr-hyper}
%\usepackage{hyperref}
%\usepackage[reqno]{amsmath}
%\usepackage{amsfonts, amsthm, amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage[parfill]{parskip}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{bm}
\usepackage{mathtools}

@@

%\newtheoremstyle{aldenthm}
%{6pt} % Space above
%{6pt} % Space below
%{\itshape} % Body font
%{} % Indent amount
%{\bfseries} % Theorem head font
%{.} % Punctuation after theorem head
%{.5em} % Space after theorem head
%{} % Theorem head spec (can be left empty, meaning `normal')

%\theoremstyle{aldenthm}
%\newtheorem{theorem}{Theorem}
%\newtheorem{definition}{Definition}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}

%\newtheoremstyle{aldenrmrk}
%{6pt} % Space above
%{6pt} % Space below
%{} % Body font
%{} % Indent amount
%{\itshape} % Theorem head font
%{.} % Punctuation after theorem head
%{.5em} % Space after theorem head
%{} % Theorem head spec (can be left empty, meaning `normal')
%
%\theoremstyle{aldenrmrk}
%\newtheorem{remark}{Remark}
%%%%%% End Alden

%\title{Local Spectral Clustering of Density Upper Level Sets}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.
%
%\author{
%Alden Green \And
%Sivaraman Balakrishnan \And
%Ryan J. Tibshirani}
%
%\begin{document}
%\maketitle
%
%\vspace{0.1in}
%\begin{abstract}

\newcommand{\widgraph}[2]{\includegraphics[keepaspectratio,width=#1]{#2}}
\newcommand{\Like}{\ensuremath{\mathcal{L}}}
\newcommand{\Ball}[2]{\mathbb{B}_{#1}(#2)}
\newcommand{\Complement}[1]{\overline{#1}}

\newcommand{\xsam}{\ensuremath{x}}
\newcommand{\samind}{\ensuremath{\ell}}
\newcommand{\Xrv}{\ensuremath{X}}
\newcommand{\Event}{\ensuremath{\mathcal{E}}}
\newcommand{\Fevent}{\ensuremath{\mathcal{F}}}

\newcommand{\usedim}{\ensuremath{d}}
\newcommand{\mubold}{\ensuremath{\boldsymbol{\mu}}}
\newcommand{\lambold}{\ensuremath{\boldsymbol{\lambda}}}
\newcommand{\sep}{\ensuremath{\xi}}
\newcommand{\mixind}{\ensuremath{i}}
\newcommand{\mixtwo}{\ensuremath{j}}
\newcommand{\nummix}{\ensuremath{M}}
\newcommand{\mustar}{\ensuremath{\mu^*}}
\newcommand{\muboldstar}{\ensuremath{\mubold^*}}
\newcommand{\muboldt}{\ensuremath{\mubold^t}}

\newcommand{\numobs}{\ensuremath{n}}
\newcommand{\SamLike}{\ensuremath{\Like_\numobs}}
\newcommand{\PopLike}{\ensuremath{\Like}}
\newcommand{\Exs}{\E}
\newcommand{\thetanew}{\ensuremath{\theta^{\text{\small{new}} }}}

\newcommand{\stepsize}{\ensuremath{s}}

\newcommand{\QMAT}{\ensuremath{\mathbf{Q}}} 
\newcommand{\DMAT}{\ensuremath{\mathbf{D}}}

\newcommand{\defn}{\ensuremath{: \, =}}
\newcommand{\muboldtilde}{\ensuremath{\tilde{\mubold}}}

%%% New version of \caption puts things in smaller type, single-spaced 
%%% and indents them to set them off more from the text.
\makeatletter
\long\def\@makecaption#1#2{
        \vskip 0.8ex
        \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
        \parindent 1.5em  %% How can we use the global value of this???
        \dimen0=\hsize
        \advance\dimen0 by -3em
        \ifdim \wd\@tempboxa >\dimen0
                \hbox to \hsize{
                        \parindent 0em
                        \hfil 
                        \parbox{\dimen0}{\def\baselinestretch{0.96}\small
                                {\bf #1.} #2
                                %%\unhbox\@tempboxa
                                } 
                        \hfil}
        \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
        \fi
        }
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center} {\Large{\bf{Local Spectral Clustering of Density Upper Level Sets}}}

\vspace*{.3cm}

{\large{
\begin{center}
Alden Green ~~~~~ Sivaraman Balakrishnan~~~~~ Ryan Tibshirani\\
\vspace{.2cm}
\end{center}

\begin{tabular}{c}
Department of Statistics and Data Science \\
Carnegie Mellon University
\end{tabular}

\vspace*{.2in}

\begin{tabular}{c}
\texttt{\{ajgreen,sbalakri,ryantibs\}@andrew.cmu.edu}
\end{tabular}
}}

\vspace*{.2in}

\today
\vspace*{.2in}

\begin{abstract}
\noindent We analyze Personalized PageRank (PPR), a local spectral method for clustering,
which extracts clusters using locally-biased random walks around a user-specified
seed node.  In contrast to previous work, we adopt a traditional statistical
learning setup, where we obtain samples from an unknown distribution, and aim to
identify connected regions of high-density (density clusters).  We prove that
PPR, run on a neighborhood graph, extracts sufficiently salient density
clusters. We also provide empirical support for our theory.
\end{abstract}
\end{center}
\section{Introduction}
\label{sec: introduction}

@@

\section{Acknowledgements}
SB is grateful to Peter Bickel, Martin Wainwright and Larry Wasserman for helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.

\appendix

%In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.

@@

	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
	\begin{align}
	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} 
	\end{align}
